Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-07 paper.qmd
Checking continuous color palattes

error_plot_two_curvy <- error_df_two_curvy_abs |>
  ggplot(aes(x = UMAP1,
             y = UMAP2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.5) +
  scale_colour_continuous_sequential(palette = "Blues") +
  coord_equal()

@@

## Compute hexbin parameters
num_bins_x_gau1 <- 13
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

@@

error_df_gau_tsne <- error_df_gau_abs |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.5) + 
  xlim(c(0.3, 0.66)) + ylim(c(-0.01, 0.35)) +
  scale_colour_continuous_sequential(palette = "Blues") +
  interior_annotation("a3", 
                      position = c(0.08, 0.9),
                      cex = 2)

@@

## Compute hexbin parameters
num_bins_x_gau1 <- 45
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

@@

>>>>

error_plot_two_curvy <- error_df_two_curvy_abs |>
  ggplot(aes(x = UMAP1,
             y = UMAP2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.5) +
  scale_colour_continuous_sequential(palette = "YlOrRd", n_interp = 10) +
  theme(
    aspect.ratio = 1
  )

@@

@@

error_df_gau_tsne <- error_df_gau_abs |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.5) + 
  xlim(c(0.3, 0.66)) + ylim(c(-0.01, 0.35)) +
  scale_colour_continuous_sequential(palette = "YlOrRd", n_interp = 20) +
  interior_annotation("a3", 
                      position = c(0.08, 0.9),
                      cex = 2)

@@

## Compute hexbin parameters
num_bins_x_gau1 <- 76
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

@@

## Compute hexbin parameters
num_bins_x_gau1 <- 33
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)
